---
title: "Intro_xkcd"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro_xkcd}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(xkcd)
library(dplyr)
library(ggplot2)
```
# xkcd

<!-- badges: start -->
<!-- badges: end -->

The `xkcd` provides an R interface to retrieve data about [xkcd comics](https://xkcd.com) from the xkcd website - and most importantly, view these comics in your plot window!

## Browsing Comics

Given a comic number the `xkcd` function retrieves a JSON object with metadata about that comic. 

```{r example}
library(xkcd)

first_comic <- xkcd(1)
first_comic
```

The most useful thing you can do with these objects is plot them, which displays the comic image in your plot window.

##Comic Data
The metadata from all 2,850 xkcd comics (thus far) is aggregated into the `xkcd_data` data set

```{r}


xkcd <- xkcd_data |>
  mutate(date = as.Date(paste(year, month, day, sep = "/")),
         weekday = weekdays(date))
```

```{r}
xkcd_published <- xkcd |>
  count(weekday)
```

```{r}
ggplot(data = xkcd_published,
       aes(x = weekday, y = n)
       ) +
  geom_col()
```

